### 2023-06-16 application.tex
up

@@

>>>>

In this section we continue to study VASS. Since they are completion-post-effective WSTS, they inherit the decidability results for WSTS in the case 
$\Safe$ is upward-closed. Lacking downward compatibility or a more relaxed hypothesis that
for all downward-closed set $D$, the set $\pred^*(D)$ is downward-closed, 
VASS do not inherit the decidability results for WSTS in the case $\Safe$ is downward-closed.
In this section, we work to re-establish decidability results for VASS when $\Safe$ is downward-closed. We also extend decidability to resilience for semilinear sets rather than simply upward and downward-closed ones.

@@

The above results concern only unbounded resilience. We consider now 
{\sc Bounded resilience} and {\sc $k$-resilience}, and focus on the length of
the path from $\Bad$ to $\Safe$
when $\Safe$ is downward-closed. Unfortunately, we have the following:
